### 2011-11-07 doc/pldi2012/highlevel.tex
Fixing a missing reference

\section{High-Level Runtime} 
\label{sec:highlevel}
In this Section we describe a high-level runtime system
that is designed to implement the Legion programming
and execution models while remaining machine agnostic.  
The high-level runtime system operates on top of the 
low-level runtime which hides machine specific details
and is described in detail in Section \ref{sec:lowlevel}.

@@

When traversing a region node, we begin by checking if there are any tasks actively using
the node.  We determine this using the pair-wise dependence analysis described 
in Section \ref{cohdep} to detect dependences between the region we are looking for and the
region represented by the current node.  For each dependence that is found, we record that the previous
task must have completed prior to the start of the task we are registering.

>>>>

\section{High-Level Runtime} 
\label{sec:highlevel}
In this Section we describe a high-level runtime system
that is designed to implement the Legion programming
and execution models while remaining machine agnostic for portability.  
The high-level runtime system operates on top of the 
low-level runtime which hides machine specific details
and is described in detail in Section \ref{sec:lowlevel}.

@@

When traversing a region node, we begin by checking if there are any tasks actively using
the node.  We determine this using the pair-wise dependence analysis described 
in Section \ref{subsec:cohdep} to detect dependences between the region we are looking for and the
region represented by the current node.  For each dependence that is found, we record that the previous
task must have completed prior to the start of the task we are registering.
